\section{Testing and Evidence}

The deterministic simulator is mandatory because Testnet cannot reliably produce all failure modes. It can script market data, partial fills, fill during cancel, cancel delay, post-only rejection, create timeout where the order actually exists, duplicate or lower cumulative fill snapshots, stale market data, stream disconnects, and reconciliation snapshots. These tests are repeatable and run without credentials.

\begin{table}[htbp]
\caption{Required scenario coverage. File names identify the main evidence source; many scenarios also have unit-level regressions.}
\label{tab:test-map}
\centering
\small
\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.11\linewidth} >{\raggedright\arraybackslash}p{0.32\linewidth} X}
\toprule
ID & Scenario & Evidence \\
\midrule
T1 & Normal Chase & \url{tests/simulation/test_required_scenarios.py::test_t1_normal_chase_submits_passive_price_and_preserves_exposure_invariant}; artifact \url{simulation/chase/exec_c8dc942476764355}. \\
T2 & Chase Reprice & \url{tests/simulation/test_required_scenarios.py::test_t2_chase_reprice_requires_threshold_and_minimum_interval}. \\
T3 & Partial Fill + Cancel Race & \url{tests/simulation/test_required_scenarios.py::test_t3_cancel_fill_race_updates_confirmed_fills_before_replacement_sizing}; script test \url{tests/simulation/test_required_scenarios.py::test_cancel_race_script_writes_required_artifacts}; artifact \url{simulation/cancel-race/exec_6106c8ca78fa4659}. \\
T4 & Create Timeout & \url{tests/simulation/test_required_scenarios.py::test_t4a_create_timeout_reconciles_to_open_order_without_new_client_order_id}; \url{tests/simulation/test_required_scenarios.py::test_t4b_create_timeout_not_found_releases_unknown_exposure_before_safe_retry}; script test \url{tests/simulation/test_required_scenarios.py::test_create_timeout_script_writes_terminal_summary_with_resolved_snapshot}; artifact \url{simulation/create-timeout/exec_048f48e8d58c4d2b}. \\
T5 & TWAP Carry-forward & \url{tests/simulation/test_required_scenarios.py::test_t5_twap_carry_forward_deficit_includes_previous_unfilled_quantity}; \url{tests/simulation/test_required_scenarios.py::test_t5b_twap_does_not_submit_before_first_absolute_slice_boundary}; artifact \url{simulation/twap/exec_61fadac604f4440a}. \\
T6 & Tail Quantity & \url{tests/simulation/test_required_scenarios.py::test_t6_tail_quantity_records_dust_and_never_rounds_up}. \\
T7 & Price Outside Range & \url{tests/simulation/test_required_scenarios.py::test_t7_price_outside_range_waits_then_expires_without_invalid_order}; \url{tests/simulation/test_required_scenarios.py::test_t7b_cancel_remainder_deadline_terminalizes_unfilled_and_partial_results}; deadline metrics \url{tests/simulation/test_required_scenarios.py::test_twap_aggressive_deadline_reports_cleanup_separately} and \url{tests/simulation/test_required_scenarios.py::test_twap_cancel_remainder_deadline_has_no_post_deadline_submissions}. \\
T8 & Stream Disconnect & \url{tests/simulation/test_required_scenarios.py::test_t8_stream_disconnect_pauses_submit_reconciles_then_resumes}. \\
T9 & Duplicate Event & \url{tests/simulation/test_required_scenarios.py::test_t9_duplicate_fill_event_does_not_double_count_cumulative_fill}. \\
T10 & Cross-zero Position & \url{tests/simulation/test_required_scenarios.py::test_t10_cross_zero_position_uses_target_minus_current_absolute_quantity}. \\
\bottomrule
\end{tabularx}
\end{table}

Current reproducible non-live baseline verification passed:

\begin{center}
\code{uv run pytest -q tests/unit tests/simulation} \quad \(\rightarrow\) \quad \code{513 passed}
\end{center}

Credentialed/network-enabled integration verification is separate: \code{uv run pytest -q tests/integration}. Those results should be reported only for a full credentialed local review where the Binance integration tests run successfully.

The four simulator scripts also ran successfully during this report build and wrote committed structured artifacts:

\begin{itemize}[leftmargin=1.2em]
  \item \code{reports/evidence/simulation/chase/exec\_c8dc942476764355}
  \item \code{reports/evidence/simulation/twap/exec\_61fadac604f4440a}
  \item \code{reports/evidence/simulation/cancel-race/exec\_6106c8ca78fa4659}
  \item \code{reports/evidence/simulation/create-timeout/exec\_048f48e8d58c4d2b}
\end{itemize}

The repository contains Binance Testnet runner scripts for Chase and TWAP. They require credentials and an explicit \code{--confirm-send-orders} flag and never fall back to simulation. Table~\ref{tab:testnet-evidence} summarizes the accepted sanitized Testnet evidence now included in the repository.

\begin{center}
\refstepcounter{table}
\label{tab:testnet-evidence}
\small\textbf{Table~\thetable: Accepted Binance Testnet evidence.}

\vspace{0.4em}
\scriptsize
\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.13\linewidth} >{\raggedright\arraybackslash}p{0.30\linewidth} X}
\toprule
Algorithm & Evidence bundle & What it proves \\
\midrule
Chase & \code{testnet/chase/exec\_3168600ee25b4193}; client ID \code{ce\_3168600ee25b\_1}; exchange order ID \code{16277695886}. & Accepted order lifecycle evidence: private user-stream events were observed, execution-matching order events were applied, final reconciliation found one order and one fill, and the execution completed with \status{COMPLETED}. \\
TWAP & \code{testnet/twap/exec\_85bef3985ea3431a}; client IDs \code{ce\_85bef3985ea3\_1}, \code{ce\_85bef3985ea3\_2}; exchange order IDs \code{16277882286}, \code{16277899689}. & Accepted TWAP evidence: two exchange orders were observed, private user-stream events were applied, the slice ledger shows carried-forward schedule deficit, final reconciliation found two orders and one fill, and the execution completed with \status{COMPLETED}. \\
\bottomrule
\end{tabularx}
\end{center}

These accepted artifacts preserve request snapshots, symbol rules, execution logs, timelines, child-order rows, fills, reconciliation output, evidence manifests, and terminal summaries while redacting \code{ACCOUNT\_UPDATE} balance and position fields. The older credentialed raw Testnet runs under \code{reports/evidence/testnet/chase} and \code{reports/evidence/testnet/twap} are retained only as rejected connectivity/error artifacts. Both reached Binance and failed before order acceptance with \code{BINANCE\_-2019:Margin is insufficient.}; both manifests have \code{accepted\_exchange\_order\_evidence=false} and empty \code{exchange\_order\_ids}.
