\section{Results and Metrics}

Each execution summary is intended to reconstruct quantity, price, order, time, and safety behavior. Table~\ref{tab:sim-results} shows selected deterministic run outputs from the committed evidence bundle under \code{reports/evidence/simulation}.

\begin{center}
\refstepcounter{table}
\label{tab:sim-results}
\small\textbf{Table~\thetable: Selected simulator results from current verification.}

\vspace{0.4em}
\small
\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.18\linewidth} X}
\toprule
Run & Result \\
\midrule
Normal Chase & \code{chase/exec\_c8dc942476764355}, child \code{ce\_c8dc94247676\_1}: one passive buy child for \(0.010\) BTC at \(50000.00\), then a simulator fill and reconciliation to \status{COMPLETED}. \\
TWAP schedule & \code{twap/exec\_61fadac604f4440a}: five \(0.002\) BTC slices over 100 seconds filled and reconciled to \(0.010\) BTC total with \code{overfill\_quantity=0}. \\
Cancel/fill race & \code{cancel-race/exec\_669d47a536a94682}: a \(0.004\) BTC fill arrived during cancel; replacement was \(0.006\) BTC, preserving total exposure at \(0.010\). \\
Create timeout & \code{create-timeout/exec\_3ddb8a47995348d0}, child \code{ce\_3ddb8a479953\_1}: unknown exposure was \(0.010\) before exact reconciliation and \(0\) after the original order was found open; no fresh client order ID was used. \\
\bottomrule
\end{tabularx}
\end{center}

Table~\ref{tab:testnet-results} gives the terminal metrics from the accepted Testnet summaries. These are not substitutes for the deterministic race tests; they prove that the same service path can read Binance rules and quotes, submit exchange-accepted orders, receive private events, reconcile by client/exchange order identifiers, and produce final execution metrics.

\begin{center}
\refstepcounter{table}
\label{tab:testnet-results}
\small\textbf{Table~\thetable: Accepted Testnet terminal metrics.}

\vspace{0.4em}
\small
\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.27\linewidth} >{\raggedright\arraybackslash}p{0.32\linewidth} X}
\toprule
Metric & Chase & TWAP \\
\midrule
Execution ID & \code{exec\_3168600ee25b4193} & \code{exec\_85bef3985ea3431a} \\
Initial to target position & \(0 \rightarrow 0.001\) BTC & \(0.0010 \rightarrow 0.005\) BTC \\
Required / filled / unfilled & \(0.001 / 0.001 / 0\) BTC & \(0.004 / 0.004 / 0\) BTC \\
Orders / cancels / reprices & \(1 / 0 / 0\) & \(2 / 1 / 0\) \\
Arrival mid / VWAP & \(62213 / 62212.5\) & \(62092.35 / 62092.9\) \\
Slippage bps & \(-0.0804\) & \(0.0886\) \\
Overfill / price violations & \(0 / 0\) & \(0 / 0\) \\
Exchange order IDs & \code{16277695886} & \code{16277882286}, \code{16277899689} \\
Requested / lifecycle duration & \(12s / 4.672s\) & \(12s / 17.295s\) \\
Decision / cleanup duration & \(4.672s / 0s\) & \(12s / 5.295s\) \\
Post-deadline scheduled / aggressive children & \(0 / 0\) & \(0 / 1\) \\
Final status / reason & \status{COMPLETED}; \code{TARGET\_QUANTITY\_FILLED} & \status{COMPLETED}; \code{TARGET\_QUANTITY\_FILLED} \\
\bottomrule
\end{tabularx}
\end{center}

The accepted TWAP Testnet run used a \(12s\) requested scheduling window and a \(17.295s\) total lifecycle. The difference is deadline cleanup: the first passive child was cancelled, private user-stream events were applied, and a bounded IOC child completed the remaining target. No passive scheduled TWAP child was submitted after the \(12s\) scheduling deadline. One deadline-aggressive child was submitted during cleanup, inside the configured price range, and completed the target with \code{overfill\_quantity=0}.

The cancel/fill race artifact is the clearest overfill evidence. The initial child was \(0.010\) BTC. During cancel, \(0.004\) BTC filled. The replacement child was only \(0.006\) BTC. The final summary showed:

\begin{center}
\small
\begin{tabular}{ll}
\toprule
Metric & Value \\
\midrule
required quantity & \(0.010\) BTC \\
confirmed filled & \(0.004\) BTC \\
live open & \(0.006\) BTC \\
reserved exposure & \(0.006\) BTC \\
unknown order & \(0\) BTC \\
client order IDs & \code{ce\_669d47a536a9\_1}, \code{ce\_669d47a536a9\_2} \\
\bottomrule
\end{tabular}
\end{center}

The create-timeout artifact demonstrates idempotency. The first child entered \status{UNKNOWN}; a subsequent run before reconciliation did not generate a new client order ID. Exact lookup found the original order and moved exposure back to live open. The final reason was \code{CREATE\_TIMEOUT\_RECONCILED}.

These examples also explain why completion rate below 100 percent can be correct. If price bounds, deadline policy, minimum quantity, post-only rejection, or venue state prevent a legal completion, the system should return actual filled and unfilled quantity with a clear reason.
